Logarithmic Space Verifiers on NP-complete

### 2019-10-26 doc/manuscript.tex
Improved content doc

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? A precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. NP is the complexity class of languages defined by polynomial time verifiers M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in P. Another major complexity classes are L and NL. The certificate-based definition of NL is based on logarithmic space Turing machine with an additional special read-once input tape: This is called a logarithmic space verifier. NL is the complexity class of languages defined by logarithmic space verifiers M such that when the input is an element of the language with its certificate, then M outputs 1. To attack the P versus NP problem, the NP-completeness is a useful concept. We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L. In this way, there is an NP-complete language which complies with an equivalent certificate-based definition of NL, and therefore P = NP.
\end{abstract}

@@

\begin{theorem}
\label{argument}
If the Hypothesis \ref{hypothesis} is true, then there is an $\textit{NP--complete}$ language which complies with an equivalent certificate-based definition of $NL$, and therefore $P = NP$.
\end{theorem}

\begin{proof}
From the early days of automata and complexity  theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}. Each model is deterministic and has a read-only input tape and some infinite work tapes \cite{KU15}. The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}. In the terminology of the (generalized) Turing machine models are called two-way and one-way deterministic Turing machines respectively \cite{KU15}.

The languages accepted by one-way deterministic logarithmic space Turing machine coincide with the class $L$ \cite{KU15}. The reason is because the classes of languages accepted by restricted and strongly $f$ space-bounded one-way deterministic Turing machine coincide, for any space constructible function $f$ on deterministic Turing machines \cite{KU15}. A function $f$ is space constructible if there exists a Turing machine $M$ which, given a string $1^{n}$ consisting of $n$ ones, outputs the binary (or unary) representation of $f(n)$, while using only $O(f(n))$ space \cite{KU15}. For the restricted and strongly mode, the space is bounded by the condition that,  given a function $f$, the Turing machine uses at most $f(i)$ cells of the work tapes in any configuration with input head at position $i$, occurring in any accepting computation \cite{KU15}. In this way, a logarithmic space computable function $f$ complies with the definition above \cite{MS06}.

In this way, we can accept the elements of the language $L_{1} \in L$ by a one-way deterministic logarithmic space Turing machine $M'$ \cite{KU15}. In addition, we can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis} by a nondeterministic logarithmic space Turing machine $N$, such that $N(w) = y$ since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}. Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space \cite{Pap03}. At the same time, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will output 1 when $w \in L_{2}$. Consequently, $M''$ is a nondeterministic logarithmic space Turing machine which accepts the language $L_{2}$.

The reason is because we can simulate the output string of $N(w)$ within a read-once output tape and thus, we can compute in logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}. Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the one-way deterministic logarithmic space Turing machine $M'$. Therefore, $L_{2}$ is in $NL$ and thus, $L_{2} \in P$ due to $NL \subseteq P$ \cite{Pap03}. If any single $\textit{NP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{CLRS01}. Since $L_{2} \in P$ and $L_{2} \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$.
\end{proof}

>>>>

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? A precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. NP is the complexity class of languages defined by polynomial time verifiers M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in P. Another major complexity classes are L and NL. The certificate-based definition of NL is based on logarithmic space Turing machine with an additional special read-once input tape: This is called a logarithmic space verifier. NL is the complexity class of languages defined by logarithmic space verifiers M such that when the input is an element of the language with its certificate, then M outputs 1. To attack the P versus NP problem, the NP-completeness is a useful concept. We demonstrate there is an NP-complete language defined by a logarithmic space verifier M such that when the input is an element of the language with its certificate, then M outputs a string which belongs to a single language in L. In this way, there is an NP-complete language which complies with the definition of NL, and therefore P = NP.
\end{abstract}

@@

\begin{theorem}
\label{argument}
If the Hypothesis \ref{hypothesis} is true, then there is an $\textit{NP--complete}$ language which complies with the definition of $NL$, and therefore $P = NP$.
\end{theorem}

\begin{proof}
From the early days of automata and complexity  theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}. Each model is deterministic and has a read-only input tape and some infinite work tapes \cite{KU15}. The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}. In the terminology of the (generalized) Turing machine models are called deterministic two-way and one-way Turing machines respectively \cite{KU15}.

The languages accepted by a deterministic one-way logarithmic space Turing machine coincide with the class $L$ \cite{KU15}. The reason is because every function $f$ that is space constructible by a deterministic two-way Turing machine, is space constructible by a strongly $f$ space-bounded deterministic one-way Turing machine as well \cite{KU15}. A function $f$ is space constructible if there exists a Turing machine $M$ which, given a string $1^{n}$ consisting of $n$ ones, outputs the binary (or unary) representation of $f(n)$, while using only $O(f(n))$ space \cite{KU15}. For the strongly mode, the space is bounded by the condition that,  given a function $f$, the Turing machine uses at most $f(i)$ cells of the work tapes in any configuration with input head at position $i$, occurring in any accepting computation \cite{KU15}. In this way, a logarithmic space computable function $f$ complies with the definition above \cite{MS06}.

In this way, we can accept the elements of the language $L_{1} \in L$ by a deterministic one-way logarithmic space Turing machine $M'$ \cite{KU15}. In addition, we can simulate the computation $M(w, u) = y$ in the Hypothesis \ref{hypothesis} by a nondeterministic logarithmic space Turing machine $N$, such that $N(w) = y$ since we can read the certificate string $u$ within the read-once tape by a work tape in a nondeterministic logarithmic space generation of symbols contained in $u$ \cite{Pap03}. Certainly, we can simulate the reading of one symbol from the string $u$ into the read-once tape just nondeterministically generating the same symbol in the work tapes using a logarithmic space \cite{Pap03}. At the same time, there is a nondeterministic logarithmic space Turing machine $M''(w) = M'(N(w))$ which will output 1 when $w \in L_{2}$. Consequently, $M''$ is a nondeterministic logarithmic space Turing machine which accepts the language $L_{2}$.

The reason is because we can simulate the output string of $N(w)$ within a read-once output tape and thus, we can compute in logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}. Certainly, we do not need to reset the computation of $N(w)$ for the reading at once of a symbol in the output string of $N(w)$ by the deterministic one-way logarithmic space Turing machine $M'$. Therefore, $L_{2}$ is in $NL$ and thus, $L_{2} \in P$ due to $NL \subseteq P$ \cite{Pap03}. If any single $\textit{NP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{CLRS01}. Since $L_{2} \in P$ and $L_{2} \in \textit{NP--complete}$, then we obtain the complexity class $P$ is equal to $NP$.
\end{proof}
